Galois Slicing as Differentiation

### 2025-07-11 main/language.tex
Tweaks.

Interpreting a whole program $\Gamma \vdash t : \tau$ yield morphisms in
$\Fam(\MeetSLat \times \JoinSLat^\op)$ which, as in \secref{semantic-gps}, are triples
$(f, \partial f_f, \partial f_r)$ of the underlying function and the forward and backward approximation
maps. However, unlike in $\Fam(\LatGal)$ are not guaranteed that the forward and backward maps even operate on
the same lattices, let alone form a Galois connection. \lemref{first-order-agreement-types} guarantees that
the lattices agree, but the fact that the pair form a Galois connection is less trivial. We will prove this
property in \secref{definability}.

>>>>

Interpreting a whole program $\Gamma \vdash t : \tau$ yield morphisms in
$\Fam(\MeetSLat \times \JoinSLat^\op)$ which, as in \secref{semantic-gps}, are triples
$(f, \partial f_f, \partial f_r)$ of the underlying function and the forward and backward approximation
maps. However, unlike in $\Fam(\LatGal)$, it is not guaranteed that the forward and backward maps even operate on
the same lattices, let alone form a Galois connection. \lemref{first-order-agreement-types} guarantees that
the lattices agree, but the fact that the pair form a Galois connection is less trivial. We will prove this
property in \secref{definability}.
